### 2009-04-07 talk/icooolps2009-dotnet/paper.tex
keyword style now is bf

\lstset{language=Python,
        basicstyle=\scriptsize\ttfamily,
        keywordstyle=\color{blue}, % I couldn't find a way to make chars both bold and tt
        frame=none,
        stringstyle=\color{blue},
        fancyvrb=true,
        xleftmargin=10pt,xrightmargin=10pt,
        showstringspaces=false}

>>>>

\lstset{language=Python,
        basicstyle=\scriptsize\ttfamily,
        keywordstyle=\bf, %\color{blue}, % I couldn't find a way to make chars both bold and tt
        frame=none,
        stringstyle=\color{blue},
        fancyvrb=true,
        xleftmargin=10pt,xrightmargin=10pt,
        showstringspaces=false}
